Data details

### 2023-05-05 analysis/data-details.qmd
Use {gt} instead of {DT}

```{r load-libraries, warning=FALSE, message=FALSE}
library(tidyverse)
library(targets)
library(DT)
library(kableExtra)
library(lubridate)

@@

@@

```{r show-iccpr}
daily_panel %>%
  filter(day == ymd("2020-06-11")) %>%
  select(country_name, iso3, day, iccpr_derogation_filed,
         derogation_start, derogation_ineffect, derogation_end) %>% 
  datatable()
```

@@

```{r show-oxford}
daily_panel %>%
  filter(day == ymd("2020-06-11")) %>%
  select(country_name, iso3, day, stringency_index, c3_cancel_events,
         c4_gatherings, c5_public_transport,
         c6_stay_at_home, c7_internal_movement,
         c8_intl_travel, e1_income_support, e2_debt_relief) %>% 
  datatable()
```

>>>>

```{r load-libraries, warning=FALSE, message=FALSE}
library(tidyverse)
library(targets)
library(sf)
library(gt)
library(kableExtra)
library(lubridate)

@@

clrs_light <- MetBrewer::met.brewer("Tiepolo") %>% colorspace::lighten(0.8)

@@

```{r show-iccpr}
#| column: page-right
daily_panel %>%
  filter(day == ymd("2020-06-11")) %>%
  select(country_name, iso3, day, iccpr_derogation_filed,
         derogation_start, derogation_ineffect, derogation_end) %>% 
  gt() %>% 
  cols_width(country_name ~ px(250),
             iso3 ~ px(60)) %>% 
  data_color(columns = contains("derogation"),
             fn = scales::col_factor(c(clrs_light[1], clrs_light[8]), 
                                     domain = c(FALSE, TRUE))) %>% 
  opt_interactive(use_compact_mode = TRUE, use_highlight = TRUE)
```

And here's a map of all the countries that derogated between January 2020 and June 2021:

```{r derogations-map, fig.width=6.5, fig.height=3.5}
ggplot() +
  geom_sf(data = derogation_map_data, aes(fill = derogations_1plus),
          linewidth = 0.1, color = "white") +
  coord_sf(crs = st_crs("+proj=robin"), datum = NA) +
  scale_fill_binned(low = colorspace::lighten(clrs[1], amount = 0.8), 
                    high = clrs[1], na.value = "grey85",
                    breaks = c(1, 5, 10, 15, 20),
                    limits = c(1, 20),
                    name = "Derogations filed: ",
                    guide = guide_colorsteps(barwidth = 7, barheight = 0.4,
                                             title.vjust = 1)) +
  theme_pandem() +
  theme(panel.border = element_blank(),
        legend.title = element_text(face = "bold"),
        legend.justification = "center")
```

@@

```{r show-oxford}
#| column: page-right
daily_panel %>%
  filter(day == ymd("2020-06-11")) %>%
  select(country_name, iso3, day, stringency_index, c3_cancel_events,
         c4_gatherings, c5_public_transport,
         c6_stay_at_home, c7_internal_movement,
         c8_intl_travel, e1_income_support, e2_debt_relief) %>% 
  gt() %>% 
  cols_width(country_name ~ px(250),
             iso3 ~ px(60),
             day ~ px(150)) %>% 
  opt_interactive(use_compact_mode = TRUE, use_highlight = TRUE)
```
